% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode

\providecommand{\home}{../..}
\documentclass[\home/main.tex]{subfiles}

\begin{document}

\chapter{Robotic folding in simulation}\label{ch:simulation}

% https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=9386154

In this chapter, we explore the use of simulation for training robotic controllers for deformable object manipulation. We frame the usage and difference of robots and physics simulators, provide a comparison between simulation technologies and implementations, and finally discuss results on learning to fold in simulation. 

\section{Digital twins}

% Why use simulation: rise of virtual env "digital twin"
Using a digital representation of a robot and the environment in which it operates allows reducing costly time on the real robot. This use-case has given rise to the name of using a \emph{digital twin} for the physical platform. This is beneficial for learning, safe experimentation and cost-effective. 

% Robot vs cloth simulation
There is a distinction to be made between physics and robotic simulations. The former is a part of robotic simulation and provides realistic modelling and simulation of physical phenomena. 

real-time vs offline.

% What do we need: our use-case 

\section{Robotic simulation {\tiny pybullet, gazebo, nvidia, v-rep, unity. Nadruk op Unity en motivatie.}}

% What is a robot simulator and how does it differ from physics simulator. Also real integrations: URDF, ROS communication with real robot. 
Robot: robot models, sensors, control algorithms. 
Rendering, headless, actuators, inverse kinematics, ROS integration 
in case of robotic maniplation, force sensing, path planning    

research simulators must have actuator models for position control, velocity control, and torque control, as these are the most commonly used modes of control for physical arms 


% Short comparison of robot simulation technologies
The popularity and success of using simulation is evident from the large landscape of available robotic simulators \autocite{Collins2021}. 

% why do we go for Unity

\section{Cloth simulation \tiny{particle system, msd, integrator , ...} }
% OP REIS TODO: schrijf particle simulation gedeelte. Lees eerst de typische papers voor structuur maar gebruik uiteindelijk muller zijn notes. 

%Zie ook "Robotic manipulation and sensing of deformable objects in domestic and industrial applications: a survey" p4 voor overzicht om te introduceren maar focus op particle based methods.
%  zie ook Dexterous Robotic Manipulation of Deformable Objects with Multi-Sensory Feedback - a Review van khalil
% background sectie 3 van SoftGym": https://arxiv.org/pdf/2011.07215.pdf
%  Voor de specifieke methode, zie ook p47 van Seita zijn boek 
%  Zie ook Muller notes about deformable object manipulation p11



\section{Learning to fold in simulation}
% hier moet ik nog wat nadenken over het doel van deze sectie 
% het demonstreren dat de simulator werkt, dat plooien kan 
% tonen dat DRL werkt maar veel iteraties nodig heeft. De reward functie is godmode en moeilijk te transfereren naar het echt 
% eventueel een behavioral cloning approach ook tonen. Dan showcasen waar het zich vastrijdt
% eventueel iets over sim2real problemen dat hier al naar boven komen 
\subsection{Deep reinforcement learning setup for cloth folding in simulation}
\subsection{Results \tiny{om te tonen dat leren mogelijk is in deze setup maar wat de moeilijkheden zijn: de reward, godmode en aantal obs}}

\footnote{The implementation of the simulation is developed in context of a software engineering course with students }


\section{Conclusion {\tiny considerations, approaches, our approach, DRL works but reward function godmode and many iterations}}

\end{document}